lab_notebook

### 2018-12-18 lab_notebook.Rmd
commmit 2/2

suppressPackageStartupMessages({
  library(tidyverse)
  library(tidyr)
  library(here)
  library(ggplot2)
  library(dplyr)
  library(readxl)
  library(devtools)
  library(plotly)
  library(base)
  library(rio)
  library(plyr)
})

@@

>>>>

suppressPackageStartupMessages({
  library(tidyverse)
  library(tidyr)
  library(here)
  library(ggplot2)
  library(dplyr)
  library(readxl)
  library(devtools)
  library(plotly)
  library(base)
  library(rio)
  library(plyr)
  library(data.table)
})

@@

ISSCAAP Codes and the non-species specific codes
```{r}

meta_isscaap_codes_1 <- join(isscaap_codes, ISSCAAP_species, by = c("SciName", "SpeciesCat"), type = "full")

meta_isscaap_codes <- unique( meta_isscaap_codes_1[ , 1:2 ] )
write_csv(meta_isscaap_codes, "meta_isscaap_codes.csv")
```

12/18/2018
Using the newly updated upside/ITQ and filtering out only the most recent date for each fishery
- make a df of these that have ITQs and those that don't -> apply to OG upside/ITQ data so that more recent years can have ITQ data
- take this new df and filter out the most recent years with ITQs and KOBE plot. also do catches

upside_2016 <- ITQ_projection %>%
  filter(Year <= "2016") %>%
  unite(id_country, IdOrig, Country, sep = "-")

upside_recent <- setDT(upside_2016)[,.SD[which.max(Year)],keyby=id_country]

upside_allfisheriesITQ <- upside_recent %>%
  select (id_country, itq, iq, ivq, Year, turf) %>%
  filter(itq != "NA" & iq != "NA" & ivq != "NA" )

#closer look at corbett's data
```{r}
Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")

corbette_recent <- setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]

corbette_fisheries <- corbette_recent %>%
  select(assess_id_short, year, speciescat, iq, itq, ivq, coop, turf)%>%
  filter(itq != "NA" & iq != "NA" & ivq != "NA" )

fisheries_with_turfs <- corbette_fisheries %>%
  filter(turf != "FALSE")

fisheries_with_itq <- corbette_fisheries %>%
   filter(itq == "TRUE" | iq == "TRUE" | ivq == "TRUE" )

reupdating upside data with new ITQ list
```{r}
#Load Data
#Upside data
projection_data <- readRDS("data/projection_data.rds")

#Update Projection with RAM
projection_updated <- join(ram, projection_data, by = c("CommName", "Year"), type = "full")

separate_projection <- projection_updated%>% 
  separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))

unite_projection <- separate_projection %>% 
  unite(assess_id_short, agency, stock, sep = "-")

colnames(fisheries_with_itq) <- c("assess_id_short", "Year","SpeciesCat" , "iq", "itq", "ivq", "coop", "turf")

fishery_itq_simple <- fisheries_with_itq %>%
  select(assess_id_short,"iq", "itq", "ivq", "turf" )

ITQ_projection_merge <- merge(unite_projection, fisheries_with_itq, by = c("assess_id_short"), all = TRUE)

recent_pre2016 <- ITQ_projection_merge %>%
  filter(Year.x <= "2016")

fisheries_recent_1 <- setDT(recent_pre2016)[,.SD[which.max(Year.x)],keyby=assess_id_short]

fisheries_recent <- fisheries_recent_1 %>%
  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq, turf)

#fisheries_recent <- write.csv(fisheries_recent, file = "fisheries_recent.csv")

##KOBE Plots with only most recent year of fisheries
RAM only
No data: ITQ = FALSE

fisheries_recent <- read_csv("data/fisheries_recent.csv")

fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"

fisheries_KOBE_ram <- fisheries_recent %>%
  filter(Dbase == "RAM") %>%
  mutate(rightsbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "0"]<- "No ITQ"
fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "1"]<- "ITQ"

F_B_graph_RAM <- ggplot(data = fisheries_KOBE_ram, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(0, 2.5)+
  xlim(0, 2.5)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  ggtitle("KOBE Plot: RAM only Fisheries")

##KOBE Plots with only most recent year of fisheries
RAM only
No data: ITQ = FALSE
```{r}

fisheries_recent <- read_csv("data/fisheries_recent.csv")

fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"

fisheries_KOBE <- fisheries_recent %>%
  mutate(rightsbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

fisheries_KOBE$rightsbased[fisheries_KOBE$rightsbased == "0"]<- "No ITQ"
fisheries_KOBE$rightsbased[fisheries_KOBE$rightsbased == "1"]<- "ITQ"

F_B_graph <- ggplot(data = fisheries_KOBE, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(0, 2.5)+
  xlim(0, 2.5)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  ggtitle("KOBE Plot:  All Fisheries")
